Bayesian exponential random graph modeling of KWL Burial network

### 2020-04-14 Note.Rmd
update the description for prior in Rmd
edit intro and download hergm

@@

>>>>

# Ergms
ERGM- consider transitivity by taking into account high-order k-triangles. Triangles and higher order cycles

@@

# acceptance rate
https://www.ibm.com/support/pages/acceptance-rate-amos-bayesian-sem
The acceptance rate is the proportion of times the Metropolis sampling algorithm generates a sample of parameter values that differs from the previous sample. For example, an acceptance rate of .2 means that, in generating a sequence of parameter values, the algorithm generates new parameter values 20% of the time and repeats the previous parameter values 80% of the time.

One rule of thumb is that the MCMC algorithm is most effective when the acceptance rate is between .2 and .5. If you see that the acceptance rate is outside this range, it may be worthwhile to try adjusting the tuning parameter. If the acceptance rate is less than .2, try making the tuning parameter smaller. If the acceptance rate is greater than .5, try making the tuning parameter larger.

### 2020-04-14 analysis/paper/paper.Rmd
edit intro and download hergm

<!--current approaches to network analysis-->
Exponential Random Graph Models (ERGMs) are an important family of statistical model for expressing properties of network structures with a focus directly on possible ties between nodes by viewing them as random variables [@Robins2007]. In traditional statistical model for network, each predictor variable for forming a tie between two nodes is measure separately by the presence of a tie without considering interactions among ties [@Morris2008]. By contrast, statistical models assumes social networks as dependent variables that can represent the network dependencies between tie variables [@Snijders2011]. In a network generated by ERGMs, the formation of a tie is influenced by the presence or absence of other ties or attributes of nodes/ties. Predictor variables, called network statistics, such as reciprocity, transitivity, homophily, are direct functions of the ties themselves where the probability of occurrence of the configuration of ties can be specified and hypothesized [@Morris2008; @Robins2007]. With the development of Markov chain Monte Carlo (MCMC) algorithms that produce approximate maximum likelihood estimators and graph statistics for further specification of transitivity and heterogeneity, ERGMs can deal with complicated dependence patterns observed at one moment in time [@Snijders2006]. The advantage of networks specification under assumptions and contexts can be useful to explain archaeological network in a given time. @Amati2019 demonstrate the use of ERGMs to reconstruct networks consist of a set of sites in the Caribbean during the period AD 100–400. They found out the structure of network can be efficiently explained by multiple interdependent mechanisms instead of hypotheses of distance and cultural homophily exclusively. However, they also point out some limitation of ERGMs

However, two major limitations ERGMs are difficult to compute because their normalizing constant depending on model parameters is intractable. A Bayesian framework allows for parameter inference using Markov chain Monte Carlo (MCMC) strategies which avoid the need for computationally intensive calculations of the normalizing constants [@Caimo2011].

@@

>>>>

<!--current approaches to network analysis-->
Exponential Random Graph Models (ERGMs) are an important family of statistical model for expressing properties of network structures with a focus directly on possible ties between nodes by viewing them as random variables [@Robins2007]. In traditional statistical model for network, each predictor variable for forming a tie between two nodes is measure separately by the presence of a tie without considering interactions among ties [@Morris2008]. By contrast, statistical models assumes social networks as dependent variables that can represent the network dependencies between tie variables [@Snijders2011]. In a network generated by ERGMs, the formation of a tie is influenced by the presence or absence of other ties or attributes of nodes/ties. Predictor variables, called network statistics, such as reciprocity, transitivity, homophily, are direct functions of the ties themselves where the probability of occurrence of the configuration of ties can be specified and hypothesized [@Morris2008; @Robins2007]. With the development of Markov chain Monte Carlo (MCMC) algorithms that produce approximate maximum likelihood estimators and graph statistics for further specification of transitivity and heterogeneity, ERGMs can deal with complicated dependence patterns observed at one moment in time [@Snijders2006]. The advantage of networks specification under assumptions and contexts can be useful to explain archaeological network in a given time. @Amati2019 demonstrate the use of ERGMs to reconstruct networks consist of a set of sites in the Caribbean during the period AD 100–400. They found out the structure of network can be efficiently explained by multiple interdependent mechanisms instead of hypotheses of distance and cultural homophily exclusively. However, they also point out some limitations of application such as static outcome and sensitive to missing data. The two major limitations ERGMs are difficult to compute because their normalizing constant depending on model parameters is intractable. A Bayesian framework allows for parameter inference using Markov chain Monte Carlo (MCMC) strategies which avoid the need for computationally intensive calculations of the normalizing constants [@Caimo2011].

@@

it can accomodate binary network statistics to describe the weighted network topology [@Snijders2006]
